Response to Pachter's Review

### 2020-02-06 index.Rmd
r

The mean number of citations per year^1.3 for signers of letter A is 6 and the median is 4.
The mean number of citations per year^1.3 for signers of letter B is 14 and the median is 9.
The mean number of citations per year^1.3 for signers of letter C is 19 and the median is 14.

>>>>

The mean number of citations per year^1.3 for signers of letter A is 6 and the median is 4.
The mean number of citations per year^1.3 for signers of letter B is 15 and the median is 9.
The mean number of citations per year^1.3 for signers of letter C is 19 and the median is 15.

### 2020-02-06 index.tex
r

The mean number of citations per year\^{}1.3 for signers of letter A is
6 and the median is 4. The mean number of citations per year\^{}1.3 for
signers of letter B is 14 and the median is 9. The mean number of
citations per year\^{}1.3 for signers of letter C is 19 and the median
is 14.

>>>>

The mean number of citations per year\^{}1.3 for signers of letter A is
6 and the median is 4. The mean number of citations per year\^{}1.3 for
signers of letter B is 15 and the median is 9. The mean number of
citations per year\^{}1.3 for signers of letter C is 19 and the median
is 15.
